(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-10 ms.tex
stellar models

>>>>

In order to try to encapsulate the effect of model uncertainties, we also run 
MCMC chains with photometric errors inflated artificially by a factor of three.  
We provide full chains using both inflated and un-inflated uncertainties, 
though in the rest of this work we adopt
the results obtained using the inflated values.
